\documentclass[../main.tex]{subfiles}
\begin{document}
\begin{thebibliography}{9}
\raggedright
%tutta da riguardare!!!
%\bibitem{definitionculture} \textit{Definition of Culture}. Merriam-Webster \url{https://www.merriam-webster.com/dictionary/culture}


\bibitem{mediator} Ropers, Norbert. \textit{Roles and Functions of Third Parties in - Berghof Foundation}.
\url{www.berghof-foundation.org/fileadmin/redaktion/Publications/Papers/Occasional\_Papers/boc14e.pdf}.

\bibitem{Pruitt} Pruitt, Dean G. \textit{Strategic Choice in Negotiation.} American Behavioral Scientist, vol. 27, no. 2, 1983, pp. 167–194., doi:10.1177/000276483027002005.

\bibitem{shell} Shell, G. Richard. \textit{Bargaining for Advantage: Negotiation Strategies for Reasonable People}. Penguin Books, 2006. Pg. 6

\bibitem{shell1} Shell, G. Richard. \textit{Bargaining for Advantage: Negotiation Strategies for Reasonable People}. Penguin Books, 2006. Pg. 27

\bibitem{culo} Ksenija Čulo, Vladimir Skendrović \textit{Communication in the Process of Negotiation}. Faculty of Civil Engineering, Josip Juraj Strossmayer University, Osijek, Croatia; World Bank, Zagreb, Croatia. 2012.

\bibitem{zartnam2} Zartman, Ira William., and Maureen R. Berman. \textit{The Practical Negotiator}. Yale Univ. Pr., 2010. Pg. 2

\bibitem{iragorri} Zartman \& Berman cit. in: Garcia Iragorri, A. \textit{International Relations as Negotiation.} (2011).  doi:10.4324/9781315633909

\bibitem{zartman3}  Zartman, Ira William., and Maureen R. Berman. \textit{The Practical Negotiator}. Yale Univ. Pr., 2010. Pg. 87

\bibitem{watershed} “Interests versus Positions.” \textit{5 Stages of Negotiation Process} | Watershed Associates, \url{https://www.watershedassociates.com/learning-center-item/interests-versus-positions.html}

\bibitem{avruch} Avruch, Kevin. \textit{Culture \& Conflict Resolution}. United States Institute of Peace Press, 2006.

\bibitem{helen} Spencer-Oatey, H. \textit{What is culture? A compilation of Quotations.} GlobalPAD Core Concepts, University of Warwick, 2012.

\bibitem{tylor} Tylor, Edward B. “Mythology (Continued).” \textit{Primitive Culture: Researches into the Development of Mythology, Philosophy, Religion, Language, Art, and Custom, Vol 1 (7th Ed.)}., pp. 316–367., doi:10.1037/13484-009.

\bibitem{andrew} Boughton, A. \textit{Cultural Impact on Negotiation.} (2009, December 29). Retrieved from \url{https://edgenegotiation.com/2009/12/cultural-impact-on-negotiation/}

\bibitem{faure} Faure, G. "The Cultural Dimensions of Negotiations: The Chinese Case." \textit{Group Decision and Negotiation} Kluver Academic Publishers, 1999

\bibitem{graham} Graham, John Lawrence. “Cross-Cultural Sales Negotiations: a Multilevel Analysis.” \textit{Thesis (Ph.D.)-University of California}, 1980.

\bibitem{albert} Mehrabian, Albert. \textit{Silent Messages: Implicit Communication of Emotions and Attitudes.} Wadsworth Pub. Co., 1981

\bibitem{zueva} Zueva, Anna, et al. "The Influence of National Culture on Negotiating Style: A New Zealand-UK Perspective." Conference Paper, Manchester Business School: University of Manchester, 2007

\bibitem{trompenaars} Trompenaars, Alfons, and Charles Hampden-Turner. \textit{Riding the Waves of Culture: Understanding Cultural Diversity in Business}. London: Nicholas Brealey, 1997.

\bibitem{hall1} Hall, Edward Twitchell. \textit{Beyond Culture}. New York, NY: Anchor Books/Doubleday, 1989. 

\bibitem{hall2} Hall, Edward Twitchell. \textit{The Dance of Life: the Other Dimension of Time}. New York, NY: Anchor Books/Doubleday, 1989.

\bibitem{hall3} Hall, Edward Twitchell. \textit{The Hidden Dimension}. New York: Doubleday, 1966.

\bibitem{salacuse} Salacuse, Jeswald W. “Ten Ways That Culture Affects Negotiating Style: Some Survey Results.” \textit{Negotiation Journal}, vol. 14, no. 3, 1998, pp. 221–240., doi:10.1111/j.1571-9979.1998.tb00162.x.

\bibitem{adair} Adair, Wendi L., and Jeanne M. Brett. “The Negotiation Dance: Time, Culture, and Behavioral Sequences in Negotiation.” \textit{Organization Science}, vol. 16, no. 1, 2005, pp. 33–51., doi:10.1287/orsc.1040.0102.

\bibitem{ferraro} Ferraro, Gary P. \textit{The Cultural Dimension of International Business}. New Jersey: 3rd ed., Prentice Hall, 1998.

\bibitem{carnevale} Carnevale, Peter J. "Property, culture, and negotiation." \textit{Negotiation as a social process}. Newbury Park: Sage, 1995.


%\bibitem{graham1} Graham, J. (1983). “Brazilian, Japanese, and American Business Negotiations,” Journal of International Business Studies, Spring/Summer 14 (1), 47–61.

\bibitem{tang} Kirkbride, Paul S., et al. “Chinese Conflict Preferences and Negotiating Behaviour: Cultural and Psychological Influences.” \textit{Organization Studies}, vol. 12, no. 3, 1991, pp. 365–386., doi:10.1177/017084069101200302.

\bibitem{rohit} Deshpande, Rohit, and Frederick E. Webster. “Organizational Culture and Marketing: Defining the Research Agenda.” \textit{Journal of Marketing}, vol. 53, no. 1, 1989, p. 3., doi:10.2307/1251521.

\bibitem{stripp} Weiss, Stephen E., and William Stripp. “Negotiating with Foreign Business Persons.” \textit{The Cultural Context in Business Communication}, 1985, p. 51., doi:10.1075/z.87.06wei.

\bibitem{faure1} Faure, Guy Olivier. “Negotiation: The Chinese Concept.” \textit{Negotiation Journal}, vol. 14, no. 2, 1998, pp. 137–148., doi:10.1111/j.1571-9979.1998.tb00154.x.

\bibitem{salacuse1} Salacuse, Jeswald W. \textit{The Global Negotiator: Making, Managing, and Mending Deals around the World in the Twenty-First Century}. Palgrave Macmillan, 2003.

\bibitem{schwartz} Schwartz, Shalom H. "A theory of cultural value orientations: Explication and applications." \textit{Comparative sociology} 5.2 (2006): 137-182.

\bibitem{sawyer} Sawyer, J., and H. Guetzkow. (1985). “ Bargaining and Negotiation in International relations,” in H. Kelman (ed.), \textit{International Behavior: A Social-Psychological Analysis}. New York: Holt, Rinehart, Winston.

\bibitem{tung} Tung, R. (1982). \textit{U.S.-China Trade Negotiations.} New York: Pergamon Press, pp 56 - 73



\end{thebibliography}
\end{document}